Processing genome scale tabular data with wormtable

### 2013-08-22 docs/paper/paper.tex
Replaced binary row format paragraph

% Wormtable's binary row format 
Data is stored in rows using a compact binary format.
Each row consists of a number of columns, and each column 
holds elements of a specific type and size.
Each column is allocated a fixed number of bytes within the `fixed region' of 
a row. For fixed
length columns, the encoded elements are stored entirely within this
fixed region; for variable length columns, the encoded elements are 
stored in the `variable region' of the row, and the location and number 
of elements stored in the fixed region. The type, size and number 
of elements of 
each column are specified in the table schema, which is defined 
in XML as part of the table's metadata.

>>>>

% Wormtable's binary row format 
Data is stored in rows using a compact binary format.
Each row consists of a defined number of columns, and each column 
holds elements of a given type and size.
Each column is allocated a fixed number of bytes within the `fixed region' of 
a row. For columns with fixed length, the encoded elements are stored entirely within the
fixed region; for columns of variable length, the encoded elements are 
stored in the `variable region' of the row, and the location and number 
of elements stored in the fixed region. The type, size and number 
of elements of 
each column are specified in the table schema, which is defined 
in XML as part of the table's metadata.
